### 2011-04-06 Spatial_adaptation/standing-variation.tex
/* Standing variation */ added info about moments of X
/* Standing variation */ latex errors

@@

We know that there are $\lamba_0$ successful standing variants per unit area;
suppose that there are $\nu_+$ successful new mutants per unit area.
Therefore, $\lambda_0+\nu_+$ is the mean number of successful mutants per unit area (duh),
and $1/(\lambda_0+\nu_+)$ is the mean area associated with a randomly chosen patch.
Let $p_0$ be the proportion of space occupied by standing variants, 
let $a_0$ be the mean area associated with a randomly chosen standing variant,
and let $a_+$ be the mean area associated with a randomly chosen new variant,
so that
\[
    p_0 = \frac{ \lambda_0 a_0 }{ \lambda_0 a_0 + \nu_+ a_+ } = \lambda_0 a_0 ,
\]
since the denominator is equal to 1.

>>>>

Let $X$ be the distance to the eventually enclosing mutation and $R=f(\tau)$ (see first paper).
Then if $g(t) = \lambda_0 \omega_d f(t)^d + \lambda h(t)$ then $(X,R)$ has density
\[
    d \omega_d x^{d-1} \exp(-g(f^{-1}(r)) dx dr,
\]
so integrating over $r$,
\[
    \P\{ X \in dx \} = dx d \omega_d x^{d-1} \int_x^\infty \exp( - g(f^{-1}(r)) ) dr ,
\]
and
\[
    \E[ X^n ] = \frac{d\omega_d}{n+d} \int_0^\infty r^{n+d} \exp( - g(f^{-1}(r)) ) dr .
\]

@@

We know that there are $\lambda_0$ successful standing variants per unit area;
suppose that there are $\nu_+$ successful new mutants per unit area.
Therefore, $\lambda_0+\nu_+$ is the mean number of successful mutants per unit area (duh),
and $1/(\lambda_0+\nu_+)$ is the mean area associated with a randomly chosen patch.
Let $p_0$ be the proportion of space occupied by standing variants, 
let $a_0$ be the mean area associated with a randomly chosen standing variant,
and let $a_+$ be the mean area associated with a randomly chosen new variant,
so that
\[
    p_0 = \frac{ \lambda_0 a_0 }{ \lambda_0 a_0 + \nu_+ a_+ } = \lambda_0 a_0 ,
\]
since the denominator is equal to 1.
